---
title: "Canarias_project-2017"
author: "NMH_people"
date: "18/05/2017"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, message = F, warning = F)
```

# Initialise analysis

```{r}
library(tidyverse)
library (ggfortify)
library(knitr)
```
We are looking at seven subspecies of a species of plant in the daisy family. All of these subspecies are found on islands in the Canary Island archipelago.

First we load the data, check it and load required packages

```{r}
canary <- read_csv("Canary_island_Argyranthemum.csv")
head(canary)


```

```{r}
a <- mutate(canary, leafratio = (leaf_length/leaf_width))

```


# Cluster analysis

The clusters have different leaf width/length ratios.

```{r}
ggplot(a, aes(x=as.factor(cluster), y=leafratio)) +
  geom_boxplot ()
```

This is confirmed using a linear model.

```{r}
model1 <- lm(leafratio ~ as.factor(cluster), data = a)
anova(model1)
summary(model1)
```
We did the Tukey test to test for differences between the clusters.

```{r}
#Tukey test to test for differences between the clusters
# according to 04_basic-stats_students.Rmd (day 03 materials)
model2.aov <- aov(model1) # repackage the model for a Tukey Test
tukey.out <- TukeyHSD(model2.aov) # generate Tukey test
tukey.ou
```



The assumptions of a parametric model are met

```{r}
autoplot(model1)
```

As might be expected, the subspecies described on the basis of morphology also differ in the leaf width/length ratio.

```{r}
ggplot(a, aes(x=subspecies, y=leafratio)) +
  geom_boxplot ()
```

