---
title: "Canarias_project-2017"
author: "NMH_people"
date: "18/05/2017"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, message = F, warning = F)
```

# Initialise analysis

```{r}
library(tidyverse)
library (ggfortify)
library(knitr)
```
We are looking at seven subspecies of a species of plant in the daisy family. All of these subspecies are found on islands in the Canary Island archipelago.

First we load the data, check it and load required packages

```{r}
canary <- read_csv("Canary_island_Argyranthemum.csv")
head(canary)


```

```{r}
a <- mutate(canary, leafratio = (leaf_length/leaf_width))

```


# Cluster analysis

The clusters have different leaf width/length ratios.

```{r}
ggplot(a, aes(x=as.factor(cluster), y=leafratio)) +
  geom_boxplot ()
```

This is confirmed using a linear model.

```{r}
model1 <- lm(leafratio ~ as.factor(cluster), data = a)
anova(model1)
summary(model1)
```

The assumptions of a parametric model are met

```{r}
autoplot(model1)
```

